---
title: "LinReg_vignette"
author: "CHEN and Aqsa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LinReg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinReg)
```

# Description
calculate the linear regression as lm()

#Usage
```R

devtools::intall_github('AqsaIftikhar25/LRLab')
```

# linreg
doing linear regression and return an object with data.

## resid()
method of the class 
return the residuals

## pred()
method of the class 
return the fitted value

## coef()
method of the class 
return the coefficients

## print()
method of the class 
return the vector of coefficients 

##summary()
method of the class 
return the results of coefficients, standard errors, t-value, p-value and the degree of freedom

## plot()
method of the class 
return the graph:

1.x--fitted value  y--residual
2.x--fitted value  y--standarized residuals

## examples
```r
lr  <-  linreg(Petal.Length~Species, data = iris)
print(lr)
plot(lr)
resid(lr)
summary(lr)

```
