---
title: "LinReg_vignette"
author: "CHEN, Aqsa and Samira"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LinReg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinReg)
```


## Description

This package is created to handle linear regression models. Function **linreg()** with two arguments *formula* and *data* return an object with of class **linreg** as an **S3** class.
Function **linreg()** calculate the linear regression as lm() and return object with a data.

## Usage

```R

devtools::intall_github('AqsaIftikhar25/LRLab')
```
## Methods

This methods of the **S3** class used in function *linreg()*:

* resid()

* pred()

* coef()

* print()

* summary()

* plot()


### resid()
This method return the residuals of a data.

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
resid(lr)
```

### pred()
This method return the fitted value of data.

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
pred(lr)
```

### coef()
This method return the coefficients of data.

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
coef(lr)
```

### print()

This method return the vector of coefficients of data.

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
print(lr)
```

### summary()
This method return the results of coefficients, standard errors, t-value, p-value and the degree of freedom.

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
summary(lr)

```

### plot()
This method return the graph:

1. x--fitted value  y--residual

2. x--fitted value  y--standarized residuals

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
plot(lr)

```

## Examples

```r
lr  <-  linreg(Petal.Length~Species, data = iris)
print(lr)
plot(lr)
resid(lr)
summary(lr)

```
